A state space model for discovering the trajectory dynamics of replay

### 2020-03-07 Article.tex
Update on Overleaf.

\section*{Results}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1/Figure1_v3.pdf}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{Figure1}
\end{figure*}

@@

\subsection*{Blabla}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Supplementary Information %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup*{format=largeformat}
\section{Something about something} \label{note:Note1} 
\Blindtext

>>>>

\section*{Results}
\subsection*{Test}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure1/Figure1_v3}
\caption{Components of the state space model and demonstration on simulated data. \textbf{(A)} 19 simulated place cells with peaks evenly spaced on a 180 cm track that exhibit three different sequence patterns. For the first third of time, one cell fires repeatedly, representing one stationary location. For the second third of time, the cells fire in sequence, representing a smooth continuous trajectory through space. For the last third cells fire in an incoherent pattern, representing a non-smooth fragmented trajectory through space. \textbf{(B)}} Like the Bayesian Decoder, the state space encoding model uses estimates of the cell's place fields to compute a likelihood of position. \textbf{(C)} 
\label{Figure1}
\end{figure*}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Supplementary Information %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\beginsupplement
\captionsetup*{format=largeformat}
